A Fredholm integral equation approach to computing Stokes eigenvalues in the plane

### 2019-03-12 doc/draft-01-stokes/03analysis2.tex
updating fredholm determinant section

\subsection{Computational Fredholm determinants}
Having established the equivalence between the Dirichlet eigenvalues
for Stokes equation and the invertibility of
the operator $\cI - 2\cD_{k} - 2\cW$ on simply connected domains, we show how 
the Fredholm determinant can be as a computational tool for detecting
the non-invertibility of $\cI - 2\cD_{k} - 2\cW$.

@@

The following lemma shows that the operator 
$-2\cD_{k} - 2\cW$ is a trace class operator.
\begin{lemma} 
$-2\cD_{k} - 2\cW$ is a trace class operator for all $k$ 
\end{lemma}
The Fredholm determinant of a second-kind Fredholm operator
is another way of detecting when the operator is not invertible. 
The following result summarizes the result. 
\begin{lemma}
If $A$ is a trace-class operator, then
\end{lemma}

>>>>

\subsection{Fredholm determinants}
Having established the equivalence between the Dirichlet eigenvalues
for Stokes equation and the invertibility of
the operator $\cI - 2\cD_{k} - 2\cW$ on simply connected domains, in this section
we show how the Fredholm determinant can be as a computational tool for detecting
the non-invertibility of $\cI - 2\cD_{k} - 2\cW$.

@@

The following lemma shows that the operator 
$-2\cD_{k} - 2\cW$ is a trace class operator.
\begin{lemma} 
$-2\cD_{k} - 2\cW$ is a trace class operator for all $k$ 
\end{lemma}
\begom{proof}
Using Bessel function asymptotics, we note that the
kernel of $\cD_{k}$ given by
$\TT_{\cdot,\cdot,\ell}\nu_{\ell}(\bx,\by)$
has a leading order singularity of $|\bx-\by|^2 \log{|\bx-\by|^2}$ as $\bx\to \by$.
It follows from~\cite{bornemann2010} numerical that $\cD_{k}$
is a trace-class operator for all $k$.
Since $\cW$ is a rank-one perturbation independent of $k$, and trace-class
operators are a vector space, we conclude that
$-2\cD_{k} - 2\cW$ is also a trace-class operator for all $k$.
\end{proof}

Let $f(k) = \text{det}(\cI - 2\cD_{k} - 2\cW)$.
We first note that $f(k)$ is an analytic function of $k$
for $k \in \mathbb{C} \setminus 0$
since the kernel of $\cD_{k}$ is an 
analytic function of $k$ on that domain, 
and the Fredholm determinant is an analytic operator.

The Fredholm determinant of a second-kind Fredholm operator
is another way of detecting when the operator is not invertible. 
The following result summarizes the result. 
\begin{lemma}
$f(k) = 0$ if and only if $\cI - 2\cD_{k} -2\cW$ 
is not invertible.
\end{lemma}
When $\Omega$ is simply connected, the above lemma combined 
with~\cref{thm:dlmain} implies $f(k) = 0$ if and only if $k$ 
is a Dirichlet eigenvalue for Stokes equation.
